Interval Probability for Fuzzy Quantum Theories

### 2016-07-02 prob.tex
prob.tex update the example, and delete redundant stuff...

\begin{definition}[Ideal Measurement; Complement;
Commutativity~\cite{Swart2013,peres1995quantum,Griffiths2003}]~
\begin{itemize}
\item A set of mutually orthogonal projections $P_{i}$ is called an \emph{ideal
measurement} if it is a partition of the identity, i.e.,
$\tensor*[_{\mathscr{O}}]{\sum}{_{i}}P_{i}=\mathbb{1}$.
\item If $P$ is a projection operator, then $\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}P$
is also a projection operator, called \emph{complement}. It is orthogonal to $P$,
and corresponds to the complement event~$\Omega\backslash E$
in classical probability.
\item Projection operators $P_{1}$ and $P_{2}$ \emph{commute} if $P_{1}P_{2}=P_{2}P_{1}$.
The product of two projection operators~$P_{1}P_{2}$ is also a projection
operator if and only if they commute. This corresponds to the classical intersection
between events. 
\item For projection operators $P_{1}$ and $P_{2}$, we define $P_{1}\tensor*[_{\mathscr{O}}]{\ge}{}P_{2}$
if $P_{1}\tensor*[_{\mathscr{O}}]{-}{}P_{2}$ is a projection operator;
and $P_{1}\tensor*[_{\mathscr{O}}]{>}{}P_{2}$ if $P_{1}\tensor*[_{\mathscr{O}}]{\ge}{}P_{2}$
and $P_{1}\ne P_{2}$. Also, let $S_{i}$ be the linear subspace $P_{i}$
project onto, then $P_{1}\tensor*[_{\mathscr{O}}]{\ge}{}P_{2}$ if
and only if $S_{1}\supseteq S_{2}$.\yutsung{Need to verify!}
\end{itemize}
\qed\end{definition}

@@

\begin{example}[Three-dimensional quantum interval-valued probability
measure] Given a three dimensional Hilbert space with an orthonormal
basis $\left\{ \ket{0},\ket{1},\ket{2}\right\} $. Consider\emph{
$\mathscr{I}=\left\{ \necess,\imposs,\unknown\right\} $}, and $\ket{\ps}=\frac{1}{\sqrt{2}}(\ket{0}+\ket{1})$
as before. Let 
\begin{eqnarray*}
\bar{\mu}(\mathbb{0})=\bar{\mu}(\proj{0})=\bar{\mu}(\proj{\ps}) & = & \imposs\textrm{ ,}\\
\bar{\mu}(\mathbb{1})=\bar{\mu}(1-\proj{0})=\bar{\mu}(1-\proj{\ps}) & = & \necess\textrm{ ,}\\
\bar{\mu}(P) & = & \unknown\textrm{, otherwise. }
\end{eqnarray*}
To verify $\bar{\mu}$ is a quantum interval-valued probability measure,
it is sufficient to check $\bar{\mu}\left(\proj{\psi_{1}}\tensor*[_{\mathscr{O}}]{+}{}\proj{\psi_{2}}\right)\subseteq\bar{\mu}\left(\proj{\psi_{1}}\right)\tensor*[_{\mathscr{I}}]{+}{}\bar{\mu}\left(\proj{\psi_{2}}\right)$
for orthogonal $\ket{\psi_{1}}$ and $\ket{\psi_{2}}$. This is easily
verified by enumerating all possible cases.

$\bar{\mu}$ cannot correspond to any quantum probability measure.
Suppose $\bar{\mu}(P)=\iota\left(\mu(P)\right)$ for some $\mu:\events\rightarrow\left[0,1\right]$.
We must have 
\begin{equation}
\mu(\proj{0})=\mu(\proj{\ps})=0\textrm{ .}\label{eq:probability-zero-on-states}
\end{equation}
By Gleason's theorem, there is a mixed state~$\rho=\sum_{j}q_{j}\proj{\phi_{j}}$
such that $\mu\left(P\right)=\sum_{j=1}^{N}q_{j}\ip{\phi_{j}}{P\phi_{j}}$,
where $\sum_{j}q_{j}=1$ and $q_{j}>0$. By
equation (\ref{eq:probability-zero-on-states}),
we have $\rho=\proj{2}$. However, 
\[
\iota\left(\mu(\proj{2})\right)=\necess\ne\unknown=\bar{\mu}(P)\textrm{ .}
\]
\qed\end{example}

@@

@@

\appendix

\section{Proof of Quantum Interval-valued Probability Measures}

In order to simplify the notation, consider the following definition
for interval-valued probability measures.

\begin{definition}Given a Hilbert space~$\Hilb$ with the set of
quantum events~$\events$, a collection of intervals~$\mathscr{I}$,
and a quantum $\mathscr{I}$-interval-valued probability measure~$\bar{\mu}:\events\rightarrow\mathscr{I}$.
Let $l:\events\rightarrow\left[0,1\right]$ and $r:\events\rightarrow\left[0,1\right]$
such that $\left[l\left(P\right),r\left(P\right)\right]=\bar{\mu}\left(P\right)$.\qed\end{definition}

Before we prove our results, we need the following lemmas.

\begin{lemma}Given a Hilbert space~$\Hilb$ with the set of quantum
events~$\events$, a collection of intervals~$\mathscr{I}$, and
a quantum $\mathscr{I}$-interval-valued probability measure~$\bar{\mu}:\events\rightarrow\mathscr{I}$.
For projection operators $P_{1}$ and $P_{2}$, if $P_{1}\tensor*[_{\mathscr{O}}]{\ge}{}P_{2}$,
then $\bar{\mu}\left(P_{1}\right)\tensor*[_{\mathscr{I}}]{\ge}{}\bar{\mu}\left(P_{2}\right)$,
where $\left[l_{1},r_{1}\right]\tensor*[_{\mathscr{I}}]{\ge}{}\left[l_{2},r_{2}\right]$
if and only if $l_{1}\tensor*[_{\mathbb{R}}]{\ge}{}l_{2}$ and $r_{1}\tensor*[_{\mathbb{R}}]{\ge}{}r_{2}$.
The preposing $\mathbb{R}$ represents its an inequality of real numbers
as usual.\qed\end{lemma}

\begin{proof}

\begin{eqnarray*}
 &  & P_{1}\tensor*[_{\mathscr{O}}]{\ge}{}P_{2}\\
 & \Rightarrow & \bar{\mu}\left(P_{1}\right)\subseteq\bar{\mu}\left(P_{1}\tensor*[_{\mathscr{O}}]{-}{}P_{2}\right)\tensor*[_{\mathscr{I}}]{+}{}\bar{\mu}\left(P_{2}\right)\\
 & \Rightarrow & l\left(P_{1}\right)\tensor*[_{\mathbb{R}}]{\ge}{}l\left(P_{1}\tensor*[_{\mathscr{O}}]{-}{}P_{2}\right)\tensor*[_{\mathbb{R}}]{+}{}l\left(P_{2}\right)\tensor*[_{\mathbb{R}}]{\ge}{}l\left(P_{2}\right)
\end{eqnarray*}
Similarly, 
\begin{eqnarray*}
 &  & \mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}P_{1}\tensor*[_{\mathscr{O}}]{\le}{}\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}P_{2}\\
 & \Rightarrow & 1\tensor*[_{\mathbb{R}}]{-}{}r\left(P_{1}\right)=l\left(\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}P_{1}\right)\tensor*[_{\mathbb{R}}]{\le}{}l\left(\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}P_{2}\right)=1\tensor*[_{\mathbb{R}}]{-}{}r\left(P_{2}\right)\\
 & \Rightarrow & r\left(P_{1}\right)\tensor*[_{\mathbb{R}}]{\ge}{}r\left(P_{2}\right)
\end{eqnarray*}

\end{proof}
\end{document}

>>>>

\begin{definition}[Ideal Measurement; Complement;
Commutativity~\cite{Swart2013,peres1995quantum,Griffiths2003}]~
\begin{itemize}
\item A set of mutually orthogonal projections $P_{i}$ is called an \emph{ideal
measurement} if it is a partition of the identity, i.e.,
$\tensor*[_{\mathscr{O}}]{\sum}{_{i}}P_{i}=\mathbb{1}$.
\item If $P$ is a projection operator, then $\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}P$
is also a projection operator, called \emph{complement}. It is orthogonal to $P$,
and corresponds to the complement event~$\Omega\backslash E$
in classical probability.
\item Projection operators $P_{1}$ and $P_{2}$ \emph{commute} if $P_{1}P_{2}=P_{2}P_{1}$.
The product of two projection operators~$P_{1}P_{2}$ is also a projection
operator if and only if they commute. This corresponds to the classical intersection
between events. 
\end{itemize}
\qed\end{definition}

@@

\begin{example}[Three-dimensional quantum interval-valued probability
measure] Given a three dimensional Hilbert space with an orthonormal
basis $\left\{ \ket{0},\ket{1},\ket{2}\right\} $. Consider\emph{
$\mathscr{I}=\left\{ \necess,\imposs,\unknown\right\} $}, $\ket{\ps}=\frac{1}{\sqrt{2}}(\ket{0}+\ket{1})$,
and $\ket{\ps'}=\frac{1}{\sqrt{2}}(\ket{0}+\ket{2})$. Let 
\begin{eqnarray*}
\bar{\mu}(\mathbb{0})=\bar{\mu}(\proj{0})=\bar{\mu}(\proj{\ps})=\bar{\mu}(\proj{\ps'}) & = & \imposs\textrm{ ,}\\
\bar{\mu}(\mathbb{1})=\bar{\mu}(1-\proj{0})=\bar{\mu}(1-\proj{\ps})=\bar{\mu}(1-\proj{\ps'}) & = & \necess\textrm{ ,}\\
\bar{\mu}(P) & = & \unknown\textrm{, otherwise. }
\end{eqnarray*}
To verify $\bar{\mu}$ is a quantum interval-valued probability measure,
it is sufficient to check $\bar{\mu}\left(\proj{\psi_{1}}\tensor*[_{\mathscr{O}}]{+}{}\proj{\psi_{2}}\right)\subseteq\bar{\mu}\left(\proj{\psi_{1}}\right)\tensor*[_{\mathscr{I}}]{+}{}\bar{\mu}\left(\proj{\psi_{2}}\right)$
for orthogonal $\ket{\psi_{1}}$ and $\ket{\psi_{2}}$. This is easily
verified by enumerating all possible cases.

$\bar{\mu}$ cannot correspond to any quantum probability measure.
Suppose $\bar{\mu}(P)=\iota\left(\mu(P)\right)$ for some $\mu:\events\rightarrow\left[0,1\right]$.
We must have 
\begin{equation}
\mu(\proj{0})=\mu(\proj{\ps})=\mu(\proj{\ps'})=0\textrm{ .}\label{eq:probability-zero-on-states}
\end{equation}
By Gleason's theorem, there is a mixed state~$\rho=\sum_{j}q_{j}\proj{\phi_{j}}$
such that $\mu\left(P\right)=\sum_{j=1}^{N}q_{j}\ip{\phi_{j}}{P\phi_{j}}$,
where $\sum_{j}q_{j}=1$ and $q_{j}>0$. However, no pure state~$\ket{\phi}$
satisfies
\[
\ip{\phi}{0}=\ip{\phi}{\ps}=\ip{\phi}{\ps'}=0
\]
so that no quantum probability measure~$\mu$ such that $\bar{\mu}(P)=\iota\left(\mu(P)\right)$.\qed\end{example}

@@

\yutsung{Is there a quantum interval-value probability measure which
corresponds to no quantum probability measure for $\mathscr{I}=\left\{ \imposs,\unlikely,\likely,\necess\right\} $?
This is still important because \emph{$\mathscr{I}=\left\{ \necess,\imposs,\unknown\right\} $}
is way to small for a general case.}

@@

\end{document}
